# File management

## Materials

`r emo::ji("books")` [**Data & materials** (on shared Box folder)](https://buffalo.box.com/s/nam5hsmqhgq02hye4tee7ujth0tut56q){target="_blank"}

- Download these materials and copy them to your local computer


## Video recording
- Please note: We went over some preliminaries on using Slack & making sure everyone had the data saved to their computer first; this part does not appear in the video

<iframe src="https://ub.hosted.panopto.com/Panopto/Pages/Embed.aspx?id=92a1a8fe-f5aa-4894-9151-acd9012767ca&autoplay=false&offerviewer=true&showtitle=true&showbrand=false&start=0&interactivity=all" height="405" width="720" style="border: 1px solid #464646;" allowfullscreen allow="autoplay"></iframe>

[Link to video](https://ub.hosted.panopto.com/Panopto/Pages/Viewer.aspx?id=92a1a8fe-f5aa-4894-9151-acd9012767ca)


## Slides
```{r echo = FALSE}
knitr::include_url("presentations/praat_scripting/UB_Praat_Scripting_workshop1.pdf")
```


# TextGrid querying

## Materials

`r emo::ji("books")` [**Data & materials** (on shared Box folder)](https://buffalo.box.com/s/nam5hsmqhgq02hye4tee7ujth0tut56q){target="_blank"}

- These are the same materials as Workshop 1
- If you haven't yet, download them and save them to your computer to follow along

## Video
<iframe src="https://ub.hosted.panopto.com/Panopto/Pages/Embed.aspx?id=763b01e5-1515-4765-b5e3-acee0113c6ff&autoplay=false&offerviewer=true&showtitle=true&showbrand=false&start=0&interactivity=all" height="405" width="720" style="border: 1px solid #464646;" allowfullscreen allow="autoplay"></iframe>

[Link to video](https://ub.hosted.panopto.com/Panopto/Pages/Viewer.aspx?id=763b01e5-1515-4765-b5e3-acee0113c6ff)

## Slides
```{r echo = FALSE}
knitr::include_url("presentations/praat_scripting/Praat Script Training Session 2 2021-03-17.pdf")
```


# Acoustic analysis

`r emo::ji("eyes")` **Watch this space!**

# PraatSauce

`r emo::ji("eyes")` **Watch this space!**
