# Materials {-}

`r emo::ji("books")` [**Data & materials for all workshops available in shared Box folder**](https://buffalo.box.com/s/nam5hsmqhgq02hye4tee7ujth0tut56q){target="_blank"}

- Download these materials and copy them to your local computer

# File management

## Video
- Please note: We went over some preliminaries on using Slack & making sure everyone had the data saved to their computer first; this part does not appear in the video

<iframe src="https://ub.hosted.panopto.com/Panopto/Pages/Embed.aspx?id=92a1a8fe-f5aa-4894-9151-acd9012767ca&autoplay=false&offerviewer=true&showtitle=true&showbrand=false&start=0&interactivity=all" height="405" width="720" style="border: 1px solid #464646;" allowfullscreen allow="autoplay"></iframe>

[Link to video](https://ub.hosted.panopto.com/Panopto/Pages/Viewer.aspx?id=92a1a8fe-f5aa-4894-9151-acd9012767ca)


## Slides
```{r echo = FALSE}
knitr::include_url("presentations/praat_scripting/Praat_scripting_1_Knowles_2021-02-24.pdf")
```


# TextGrid querying

## Video
<iframe src="https://ub.hosted.panopto.com/Panopto/Pages/Embed.aspx?id=763b01e5-1515-4765-b5e3-acee0113c6ff&autoplay=false&offerviewer=true&showtitle=true&showbrand=false&start=0&interactivity=all" height="405" width="720" style="border: 1px solid #464646;" allowfullscreen allow="autoplay"></iframe>

[Link to video](https://ub.hosted.panopto.com/Panopto/Pages/Viewer.aspx?id=763b01e5-1515-4765-b5e3-acee0113c6ff)

## Slides
```{r echo = FALSE}
knitr::include_url("presentations/praat_scripting/Praat_scripting_2_Heffner_2021-03-17.pdf")
```


# Acoustic analysis & extraction

## Video
<iframe src="https://ub.hosted.panopto.com/Panopto/Pages/Embed.aspx?id=14afe3d1-847f-4d47-a894-ad03014c6f77&autoplay=false&offerviewer=true&showtitle=true&showbrand=false&start=0&interactivity=all" height="405" width="720" style="border: 1px solid #464646;" allowfullscreen allow="autoplay"></iframe>

## Slides
```{r echo = FALSE}
knitr::include_url("presentations/praat_scripting/Praat_scripting_3_Dicanio_2021-04-07.pdf")
```

# PraatSauce


[PraatSauce](https://github.com/kirbyj/praatsauce) is a set of Praat Scripts written by James Kirby designed to facilitate extraction of spectral measures from acoustic data.
 
Christian and Thea gave an overview of voice quality considerations cross-linguistically and in clinical populations. We briefly discussed the two papers below. Christian gave an "unboxing" demo of PraatSauce and then he and Thea demo'd it on their own data. The video of this workshop only includes the PraatSauce demo.

## Demo video
<iframe src="https://ub.hosted.panopto.com/Panopto/Pages/Embed.aspx?id=b1b87a70-94e9-40ea-8fcd-ad18010cce14&autoplay=false&offerviewer=true&showtitle=true&showbrand=false&start=0&interactivity=all" height="405" width="720" style="border: 1px solid #464646;" allowfullscreen allow="autoplay"></iframe>

## Voice quality presentations
Note: If you want to be able to hear the audio clips used in Christian's presentation, you'll need a copy of the Voice_quality_presentation folder from Box.

```{r echo = FALSE}
knitr::include_url("presentations/praat_scripting/Voice_quality_praatsauce copy.pdf")
```

```{r echo = FALSE}
knitr::include_url("presentations/praat_scripting/VQ_dysarthria.pdf")
```

## Papers for discussion

1. [Brunelle et al., 2020](https://www.journal-labphon.org/article/10.5334/labphon.278/) 
2. [Kirby & Hyslop, 2019](https://assta.org/proceedings/ICPhS2019/papers/ICPhS_3656.pdf)

