# Materials {-}

`r emo::ji("books")` [**Data & materials for all workshops available in shared Box folder**](https://buffalo.box.com/s/nam5hsmqhgq02hye4tee7ujth0tut56q){target="_blank"}

- Download these materials and copy them to your local computer

# File management

## Video recording
- Please note: We went over some preliminaries on using Slack & making sure everyone had the data saved to their computer first; this part does not appear in the video

<iframe src="https://ub.hosted.panopto.com/Panopto/Pages/Embed.aspx?id=92a1a8fe-f5aa-4894-9151-acd9012767ca&autoplay=false&offerviewer=true&showtitle=true&showbrand=false&start=0&interactivity=all" height="405" width="720" style="border: 1px solid #464646;" allowfullscreen allow="autoplay"></iframe>

[Link to video](https://ub.hosted.panopto.com/Panopto/Pages/Viewer.aspx?id=92a1a8fe-f5aa-4894-9151-acd9012767ca)


## Slides
```{r echo = FALSE}
knitr::include_url("presentations/praat_scripting/Praat_scripting_1_Knowles_2021-02-24.pdf")
```


# TextGrid querying

## Video
<iframe src="https://ub.hosted.panopto.com/Panopto/Pages/Embed.aspx?id=763b01e5-1515-4765-b5e3-acee0113c6ff&autoplay=false&offerviewer=true&showtitle=true&showbrand=false&start=0&interactivity=all" height="405" width="720" style="border: 1px solid #464646;" allowfullscreen allow="autoplay"></iframe>

[Link to video](https://ub.hosted.panopto.com/Panopto/Pages/Viewer.aspx?id=763b01e5-1515-4765-b5e3-acee0113c6ff)

## Slides
```{r echo = FALSE}
knitr::include_url("presentations/praat_scripting/Praat_scripting_2_Heffner_2021-03-17.pdf")
```


# Acoustic analysis & extraction

## Video
<iframe src="https://ub.hosted.panopto.com/Panopto/Pages/Embed.aspx?id=14afe3d1-847f-4d47-a894-ad03014c6f77&autoplay=false&offerviewer=true&showtitle=true&showbrand=false&start=0&interactivity=all" height="405" width="720" style="border: 1px solid #464646;" allowfullscreen allow="autoplay"></iframe>

## Slides
```{r echo = FALSE}
knitr::include_url("presentations/praat_scripting/Praat_scripting_3_Dicanio_2021-04-07.pdf")
```
# PraatSauce
`r emo::ji("eyes")` **Watch this space for more info!**

 [PraatSauce](https://github.com/kirbyj/praatsauce) is a set of Praat Scripts written by James Kirby designed to facilitate extraction of spectral measures from acoustic data.
 
 Christian & Thea will each demo PraatSauce on a subset of their own data. We will also briefly discuss the two papers below.

## Papers for discussion

1. [Brunelle et al., 2020](https://www.journal-labphon.org/article/10.5334/labphon.278/) 
2. [Kirby & Hyslop, 2019](https://assta.org/proceedings/ICPhS2019/papers/ICPhS_3656.pdf)
